Market-based Mechanisms for Resource Scheduling

### 2013-12-18 paper/paper.tex
Misc. changes

\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%

@@

Users have time-varying demands and tasks of varying importance.
Users can apply additional computational resources to speed up a task (e.g. via speculative execution)
Users face deadlines.
Different resources are inhomogeneous, and tasks have inhomogeneous sensitivity to characteristics of resources. Either the scheduler does not make decisions on the basis of these inhomogeneities, or different resources are imperfect substitutes.

@@

If user $i$ values jobs more in phase 2, it is easy to verify that any allocation which is both Pareto efficient and compatible with the sharing incentive must give user $i$ 
more resources than user $j$ in phase 2 and (consequently) fewer resources than user $j$ in phase 1. 
Since the scheduler must decide which user to give more resources in phase 1, it cannot possibly be Pareto efficient and compatible with the sharing incentive in both cases. \qed
\end{pproof}

@@

Summing over all rounds of the auction, A values the total resources they receive at at least the amount they pay for them, 
and user A values the total resources others receive at at most the amount that others pay for them. The desired result follows immediately. \qed
\end{pproof}

@@

This contradicts the assumption that $(R_1, p_1)$ was the result of running the auction with bid $B_1$. \qed 
\end{pproof}
\vspace{-5mm}
We must also weaken the notion of Pareto efficiency in order for it to be achievable (see Theorem~\ref{no-efficiency})
\vspace{-5mm}
\begin{theorem}[Local Pareto efficiency.]
If users bid honestly, 
there is no way to change the tasks which are scheduled at a single time $T$ in a way which makes every user better off.
\end{theorem}
\vspace{-5mm}
\begin{pproof}
At each individual time $T$, the allocation selected is chosen precisely to maximize welfare using the stated preferences of bidders. 
Consequently, assuming that bidders honestly report their welfare, the allocation which is selected maximizes welfare. \qed
\end{pproof}

\begin{table}[t!]
%\begin{center}
    \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    Desired & \small DRF & \small DRF & \small Market-based  \\
    Properties & \small(simple) & \small (realistic) & \small Mechanism \\
    \hline
    \small Envy-Free & \cmark &  & Locally\footnote{No framework envies a framework that pays less.} \\
    \small Pareto-Efficient & \cmark & Locally\footnote{With caveats arising from computational hardness of packing problems.} & Locally\footnote{With caveats arising from computational hardness of packing problems}  \\
    \small Strategy-proof & \cmark & Locally  & Locally \\
    \small Sharing incentive & \cmark &  & \cmark\\
    \hline
    \end{tabular}
%\end{center}
  \caption{Properties of DRF in a simple environment
 compared with properties of DRF and our economic mechanism
 in a more realistic environment (see section~\ref{drawbacks}).}
  \label{table:props}
\end{table}

@@

\section{Acknowledgment}

>>>>

\usepackage{amsmath}
\usepackage{caption}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%

@@

\begin{itemize}
\item Users have time-varying demands and tasks of varying importance.
\item Users can apply additional computational resources to speed up a task (e.g. via speculative execution)
\item Users face deadlines.
\item Different resources are inhomogeneous, and tasks have inhomogeneous sensitivity to characteristics of resources. Either the scheduler does not make decisions on the basis of these inhomogeneities, or different resources are imperfect substitutes.
\end{itemize}

@@

If user $i$ values jobs more in phase 2, it is easy to verify that any allocation which is both Pareto efficient and compatible with the sharing incentive must give user $i$ 
more resources than user $j$ in phase 2 and (consequently) fewer resources than user $j$ in phase 1. 
Since the scheduler must decide which user to give more resources in phase 1, it cannot possibly be Pareto efficient and compatible with the sharing incentive in both cases. \qed
\qed
\end{pproof}

@@

Summing over all rounds of the auction, A values the total resources they receive at at least the amount they pay for them, 
and user A values the total resources others receive at at most the amount that others pay for them. The desired result follows immediately. \qed
\qed
\end{pproof}

@@

This contradicts the assumption that $(R_1, p_1)$ was the result of running the auction with bid $B_1$. \qed 
\qed
\end{pproof}
\vspace{-5mm}
We must also weaken the notion of Pareto efficiency in order for it to be achievable (see Theorem~\ref{no-efficiency})
\vspace{-5mm}
\begin{theorem}[Local Pareto efficiency.]
If users bid honestly, 
there is no way to change the tasks which are scheduled at a single time $T$ in a way which makes every user better off.
\end{theorem}
\vspace{-5mm}
\begin{pproof}
At each individual time $T$, the allocation selected is chosen precisely to maximize welfare using the stated preferences of bidders. 
Consequently, assuming that bidders honestly report their welfare, the allocation which is selected maximizes welfare. \qed
\qed
\end{pproof}

\begin{table}[t!]
%\begin{center}
    \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    Desired & \small DRF & \small DRF & \small Market-based  \\
    Properties & \small(simple) & \small (realistic) & \small Mechanism \\
    \hline
    \small Envy-Free & \cmark &  & Locally* \\
    \small Pareto-Efficient & \cmark & Locally** & Locally**   \\
    \small Strategy-proof & \cmark & Locally  & Locally \\
    \small Sharing incentive & \cmark &  & \cmark\\
    \hline
    \end{tabular}
%\end{center}
  \caption{Properties of DRF in a simple environment
 compared with properties of DRF and our economic mechanism
 in a more realistic environment (see section~\ref{drawbacks}).}
\caption*{* No framework envies another framework that pays less.}
\caption*{** Modulo difficulties resulting from indivisibility of tasks / computational
hardness of packing problems.}
  \label{table:props}
\end{table}

@@

\section{Acknowledgments}
